SeedLing: Building and using a seed corpus \\ for the Human Language Project

### 2014-03-22 docs/computEL/paper.tex
updates to abstract

@@

\begin{document}
\maketitle
\begin{abstract}
\textcolor{blue}{[revisit abstract]}
Computational study of endangered languages is constrained by the lack of digitally-available data. Existing corpora are limited in the range of languages covered, in standardisation, or in machine-readability.
This makes the situation even worse for the computational linguist, especially one who would like to take a cross-linguistic or typological approach. We first survey existing efforts to compile cross-linguistic resources, then describe our own approach and give an example application - language clustering. To build the foundation text for a Universal Corpus, we crawled and cleaned texts from several web sources that contain data from a large number languages, and converted them into a standardised form consistent with the guidelines set out by \newcite{abney2010universal}. The resulting corpus is more easily-accessible and machine-readable than any of the underlying data sources, and represents a significant base corpus for researchers to draw on and add to in the future.
\end{abstract}

>>>>

\newcommand{\bluenote}[1]{\textcolor{blue}{[#1]}}

@@

\begin{document}
\maketitle
\begin{abstract}
  A bread-coverage corpus such as the Human Language Project
  envisioned by \newcite{abney2010universal} would be a powerful
  resource for the study of endangered languages.
%, \bluenote{keep? from
 %   the perspective of both the documentary and the computational
  %  linguist}. 
Existing corpora are limited in the range of languages
  covered, in standardisation, or in machine-readability. In this
  paper we present SeedLing, a seed corpus for the Human Language
  Project. We first survey existing efforts to compile
  cross-linguistic resources, then describe our own approach. To build
  the foundation text for a universal corpus, we crawl and clean
  texts from several web sources that contain data from a large number
  of languages, and convert them into a standardised form consistent
  with the guidelines set out by \shortcite{abney2010universal}. The
  resulting corpus is more easily-accessible and machine-readable than
  any of the underlying data sources, and represents a significant
  base corpus for researchers to draw on and add to in the future. To show the utility of SeedLing for cross-lingual computational research, we use our data in the test application of clustering similar languages.
\end{abstract}
